\chapter{Introduction}
    \section{Terms and Definitions}
    %
        \subsection*{Buoyancy force}\label{sec:Buoyancy force}
        %
        A body submerged in a fluid experiences a force anti-parallel to the gravitational force and proportional to the
        mass of the fluid displaced.
        %
        \subsection*{Surface Tension}
        %
        In a simplified manner attracting intermolecular interactions inside a fluid can be seen as isotrope. Thus,
        they cancel each other out. The closer a particle gets to the interfacing layer of another medium the fewer neighbors
        there are to exert attracting forces from that direction. The attracting force a particle along the interfacing
        layer experiences nets to a force normal to the interface layer and directed inside the fluid.
        %
        \subsection*{Surfactant}
        %
        A material or compound able to alter or even nullify the intermolecular forces inside a fluid (typically a liquid).
        %
        \subsection*{\textsc{Du Noüy}-Method to Measure the Surface Tension of a Liquid}
        %
        \subsection*{Other Ways to Measure the Surface Tension of a Liquid}
        %
        \subsection*{Working Principle of a Strain Gauge}
        %
        Stress induced change of the geometry of a strain gauge translates to a change of its resistance. The impossibility
        to measure electrical resistance directly it typically gets transduced to a voltage signal in order to be further
        processed.
        %
        \subsection*{Working Principle of an Instrumentation Amplifier}
        %
        \subsection*{Resolution of an Analog-Digital Converter}
        %
        An analog-to-digital converter (hereafter referred to as ADC) converts a continuous to a discrete, bitwise signal.
        The number of fractions the ADC is able to divide a given signal to gives the resolution of that ADC.
        %
    \section{Preparation}
    %
        \subsection*{Force-Time-Curve}\label{sec:A1 force time curve}% A1
        %
            In fig. 4 the force-time-diagram is subdivided into the following 8 parts:
            \begin{enumerate}
                \item The ring is located above the interface. No force is caused.
                \item The ring touches the interface, creating a small positive adhesive force between the ring and the surface.
                \item The ring is about to penetrate the surface while the surface tension creates a small negative force.
                \item The ring is now immersed. Its wires produce a small positive force.
                \item When diving upwards, the force gradually increases.
                \item The ring breaks through the interface and induces an ever-increasing force.
                \item The force reaches its maximum.
                \item The force decreases a bit with the raising until the lamella collapses.
            \end{enumerate}
            If the diagram is compared with that in fig. 14, some differences are noted. For example, there are small
            periodic vibrations that probably have to do with the fluctuation of the ring and other external influences.
            It is particularly noticeable that after penetrating the surface, the force does not rise again into the
            positive, but remains in the negative and only returns into the positive from step 6. Otherwise, from a
            qualitative point of view, everything is similar to that in fig. 4, except that after the lamella has
            collapsed, the force oscillates around the zero position.
            %
        \subsection*{Surface Tension Formula}\label{sec:A2 derive eq.4}% A2
        %
            The changing Area $ \Delta A $ corresponds to the inner plus outer circumference $ r_i $ and $ r_a $ of
            the ring multiplied by the changing height $ \Delta x $:
            \begin{align}
                \Delta A = 2\pi \cdot (r_i + r_a) \cdot \Delta x
            \end{align}
            Since the diameter $ D = 2R $ of the ring is much longer than the thickness $ t = r_a - r_i $, it can be assumed
            that the inner and outer circumferences are equal. It results:
            \begin{equation}
                \begin{gathered}
                    2R \gg r_a-r_i \quad \Rightarrow \quad r_i \approx r_a \approx R \\
                    \Leftrightarrow \\
                    \Delta A = 4\pi \cdot R \cdot \Delta x
                \end{gathered}
            \end{equation}
            %
        \subsection{Gravitational Force of the \textsc{Du Noüy}-Ring in Water and Air}\label{sec:A3 gravi force of du noüy ring}% A3
            %
            Air:

            \begin{equation}
                F_{Ring,Air} = -m_{Ring} \cdot g
            \end{equation}

            Water:

            \begin{align}
                F_{Ring,H_2O}  &= \left( m_{H_2O} - m_{Ring}\right) \cdot g \nonumber \\
                                &= \left(\rho_{H_2O} - \rho_{Al}\right)V_{Ring} \cdot g
            \end{align}
            %
        \subsection{Deriving an Equation for \( U_{Br}(\nicefrac[]{\Delta l}{l}) \)}\label{sec:A4 equation for full bridge circuit}% A4
        %
            \begin{equation}
                U_{Br} = U_2 - U_4 = U_3 - U_1 \quad \text{with} \quad U_{Br} = 0 \text{for} \frac{R_1}{R_2} = \frac{R_3}{R_4}
            \end{equation}
            \begin{equation}
                U_{Br} = U_2 - U_4 = U_0 \cdot \left(\frac{R_2}{R_1 + R_2} - \frac{R_4}{R_3 + R_4}\right)
            \end{equation}
            Defining
            \begin{align}
                R_2 &= R_3 = R + \Delta R \\
                R_1 &= R_4 = R - \Delta R
            \end{align}
            leads to
            \begin{align}
                U_{Br}  &= U_0 \cdot \left(\frac{R + \Delta R}{R - \Delta R + R + \Delta R} - \frac{R - \Delta R}{R + \Delta R + R - \Delta R}\right) \nonumber \\
                        &= U_0 \cdot \left(\frac{R+\Delta r}{2R} + \frac{-R + \Delta R}{2R}\right) \nonumber \\
                        &= U_0 \cdot \frac{\Delta R}{R}
                \label{eq:Ubr and delta R}
            \end{align}
            thus, the bridge voltage is linearly proportional to the factor \( \frac{\Delta R}{R} \).\par
            Now, with the knowledge that the resistance of a body relates with its geometry by
            \( R = \varrho \cdot \frac{l}{b \cdot d} \) and the change of its dimensions under stress follow
            %
            \begin{equation}
                \frac{\Delta b}{b} = -\nu \frac{\Delta l}{l}, \quad \frac{\Delta d}{d} = -\nu \frac{\Delta l}{l}
            \end{equation}
            the bridge voltage can be expressed as
            \begin{align}
                U_{Br} = U_0 \cdot \left( \frac{\Delta s}{s} + \nu \cdot \frac{3 \Delta l}{l}\right)
            \end{align}
            %
        \subsection{Schematic Diagram of a Full Bridge}\label{sec:A5 schematic diagram full bridge}% A5
        %
        \subsection{Characteristics of HX711}\label{sec:A6 characteristics of the HX711}% A6
        %
            \begin{align}
                &\text{Resolution:}             &&n = \SI{24}{bit}\\
                &\text{Full-scale range:}       &&U_{FSR} = \pm \SI{20}{mV}\\
                &\text{Minimum voltage change:} &&U_{LSB} = U_{FSR} \cdot 2^{-24} \approx \SI{1.2}{nV}
            \end{align}
            %
        \subsection{Impact of Statistical Effects on the effective Resolution}\label{sec:A7 statistical effects}% A7
        %
        The resolution \( n \) of an ADC as per specification implies an ideal, i.e. free-of-noise dc signal. The effective resolution —
        or ENOB (\textbf{E}ffective \textbf{N}umber \textbf{O}f \textbf{B}its) — can be calculated by \cref{eq:ENOB}
        \begin{equation}
            ENOB = n - \log_2{\sigma}
            \label{eq:ENOB}
        \end{equation}
        where \( \sigma \) is the RMS (\textbf{R}oot \textbf{M}ean \textbf{S}quare) or standard deviation of the signals noise.
        %
        \subsection{Step Response of an Exponential Filter}\label{sec:A8 step response expo filter}% A8
        %
        \subsection{Simulation of the Filter Algorithm}\label{sec:A9 simu of the filter algo}% A9
        %
        \subsection{Expected Forces}\label{sec:A10 expected forces}% A10
        %