\chapter{Conclusion}
When performing the experiment, there were the usual problems with RealTerm at first. However, these were soon solved. The further performing of the experiment according to the instructions did not cause any problems on the whole. A device that would have made it easier to bring the Du Noüy ring into the horizontal and hold it there, as well as a lifting platform that could be moved more evenly, would have been desirable. During the evaluation, unfortunately, a systematic error was found in the calibration of the force sensor. In order to enable an evaluation at all, the calibration factor had to be determined with the aid of the literature value for distilled water from the measurements with distilled water. This meant that the value for the surface tension of distilled water could not be determined retrospectively. However, the surface tensions of water with detergent and of 2-isopropanol could be determined as intended.\\
The stray diagrams from the measurements without additional weight showed the expected curve, i.e. the raw data have a larger scatter. This is also reflected in the histograms in the form of the lower binning for the filtered data.\\
The Du Noüy ring method gave the characteristic curve with the 8 areas for the dipping phase and the pulling out. The force calculated in the preparation section to cause the lamella to tear and the mean value from the experimentally determined value agrees in a good approximation.\\
The determined surface tensions fit pretty well with the literature values at all. The fact that the surface tension is decreasing with more detergent is also plausible. Except for the distilled water, the error areas do not cover the literature values. The reason for this is that the calculated deviation of the force is way too small to be assumed as the uncertainty. The deviation calculation of the surface tension implies that the ring radius uncertainty is incorrectly weighted more heavily than that of the force. For the force uncertainty the standard deviation should have been taken.\\
Overall, the recorded curves looked as expected. Partly there are uncleanliness which are visible in the curves. They are due to the construction and the sometimes rough execution.
